An Efficient Forecasting Approach for the Real-Time Reduction of Boundary Effects in Time-Frequency Representations

### 2020-07-10 Notes/results.tex
code

On Fig.~\ref{fig:res.noise.sine}, we display the experimental variance $\gamma_{\xp}[N-1+\ell,N-1+\ell]$ for each value of $\sigma$. The associated theoretical asymptotic forecasting variance~\eqref{eq:cov.error.2} is also displayed in solid line. As expected, this result highlights the fact that the forecasting variance increases linearly with respect to $\sigma^2$. Surprisingly, this result shows that the forecasting variance {\em slightly} decreases with $\ell$, what is counterintuitive. 
%
{\color{red} [HT: need a more convincing explanation.] } 
%It should be noted that, contrary to what expression~\eqref{eq:cov.error.2} suggests, smaller values of $\sigma$ do not cause a decrease of the experimental variance, but an increase. This comes from the fact that when $\sigma$ is small, the matrix $\bX\bX^T$ becomes ill-conditioned. The calculation of the forecasting matrix $\tilde\bA$ in~\eqref{eq:lse} is then strongly disturbed.

@@

>>>>

On Fig.~\ref{fig:res.noise.sine}, we display the experimental variance $\gamma_{\xp}[N-1+\ell,N-1+\ell]$ for each value of $\sigma$. The associated theoretical asymptotic forecasting variance~\eqref{eq:cov.error.2} is also displayed in solid line. As expected, this result highlights the fact that the forecasting variance increases linearly with respect to $\sigma^2$. Surprisingly, this result shows that the forecasting variance {\em slightly} decreases with $\ell$, what is counterintuitive. 
%
%{\color{red} [HT: need a more convincing explanation.] } 
%It should be noted that, contrary to what expression~\eqref{eq:cov.error.2} suggests, smaller values of $\sigma$ do not cause a decrease of the experimental variance, but an increase. This comes from the fact that when $\sigma$ is small, the matrix $\bX\bX^T$ becomes ill-conditioned. The calculation of the forecasting matrix $\tilde\bA$ in~\eqref{eq:lse} is then strongly disturbed.

@@

Finally, in order to verify the ability of {\sf BoundEffRed} to be implemented in real time, we evaluate the computation time required for each iteration of Algorithm~\ref{alg:boundary}, corresponding to the update of the boundary-free TF representation. This check is performed on the real-time SST of a 10-minute sample of the respiratory signal. As the SST is temporally sub-sampled by a ratio of 10, the update should not exceed $10/\fs=0.1$~sec. This is indeed the case, as no iteration lasted longer than xx sec on a 6-Core Xeon CPU running at 3.5~GHz and 64~GB of RAM.
